\documentclass[12pt,bibliography=totoc,final]{scrbook} %11pt+=oneside
\usepackage{a4} \linespread{1.2} \usepackage[all,2cell]{xy} \UseAllTwocells
\usepackage{stmaryrd}\usepackage{bbm} %defines \mathbbm, thus \mathbbm{1}
\usepackage{amsmath,amssymb,amsfonts,amsthm} \usepackage[english]{babel} \usepackage[final]{hyperref} \usepackage{mathtools}
%\usepackage{fancyhdr} \usepackage{lscape}

\newtheorem{thm}{Theorem}[section] \newtheorem{lem}[thm]{Lemma} \newtheorem{prop}[thm]{Proposition} \newtheorem{cor}[thm]{Corollary} \theoremstyle{definition}
\newtheorem{Remi}[thm]{Reminder} \newtheorem{rem}[thm]{Remark} \newtheorem{defn}[thm]{Definition} \newtheorem{ex}[thm]{Example} \newtheorem{conj}[thm]{Conjecture}
\def\div{\mathrm{div}} \def\mod{\mathrm{mod}} \def\Ob{\mathrm{Ob}} \def\A{\mathcal{A}} \def\C{\mathcal{C}} \def\D{\mathcal{D}} \def\V{\mathcal{V}} \def\K{\mathcal{K}}
\def\l{\ell} \def\L{\mathcal{L}} \def\R{\mathcal{R}} \def\RR{\mathbb{R}} \def\M{\mathcal{M}(\mathcal{R})} \def\MM{\mathcal{M}} \def\CC{\mathbb{C}} \def\fC{\mathfrak{C}}
\def\P{\mathbb{P}} \def\S{\mathbb{S}} \def\H{\mathbb{H}} \def\E{\mathbb{E}} \def\F{\mathbb{F}} \def\Aix{A_+\downarrow\mathrm{Fin}_+} \def\Bix{B_+\downarrow\mathrm{Fin}_+}
\def\Fi{\mathrm{Fin}_+} \def\Fia{\mathrm{Fin^{As}_{+}}} \def\Ep{\mathrm{Epi}_+} \def\barF{\overline{\mathbb{F}}}
\def\cp{\boxempty} \DeclareMathOperator{\id}{id} \DeclareMathOperator{\im}{im} \DeclareMathOperator{\sk}{sk} \DeclareMathOperator{\cosk}{cosk} 
\DeclareMathOperator{\colim}{colim} \DeclareMathOperator{\const}{const} \DeclareMathOperator{\hocolim}{hocolim} \DeclareMathOperator{\holim}{holim}
\renewcommand{\S}{\ensuremath{\mathbb{S}}} \newcommand{\Z}{\ensuremath{\mathbb{Z}}} \newcommand{\N}{\ensuremath{\mathbb{N}}} 
\newcommand{\SymMonCat}{\mathcal{S}\mathrm{ym}\mathcal{M}\mathrm{on}\mathcal{C}\mathrm{at}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil} \DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\def\arxiv#1{\href{http://arxiv.org/abs/#1}{\texttt{arxiv:#1}}} \def\arxivold#1{\href{http://arxiv.org/abs/math/#1}{\texttt{arxiv:#1}}}


\newcommand*{\titleGP}{\begingroup % Create the command for including the title page in the document
\thispagestyle{empty}\clearpage\thispagestyle{empty}\clearpage

\begin{center} % Center all text
\vspace*{\baselineskip} % White space at the top of the page

\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal line
\rule{\textwidth}{0.4pt}\\[\baselineskip] % Thin horizontal line

{\LARGE MULTIPLICATIVE STRUCTURES\\ AND INVOLUTIONS ON \\[0.3\baselineskip] ALGEBRAIC $K$--THEORY}\\[\baselineskip] % Title

\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal line
\rule{\textwidth}{1.6pt}\\[\baselineskip] % Thick horizontal line

{{\scshape % Small caps
Dissertation with the aim of achieving a doctoral degree
at the \\ Faculty of Mathematics, Informatics and Natural Sciences,
Department of Mathematics \\% Tagline(s) or further description
of Universit{\"a}t Hamburg \vfill}
Submitted by: Marc Lange \\ 
{2015} in Hamburg}

\end{center}
\endgroup}

\date{\the\day.\the\month.\the\year}

\begin{document}
\pagestyle{empty}\titleGP \null\newpage \null\vfill Als Dissertation angenommen vom Fachbereich \\
Mathematik der Universit\"at Hamburg\\[2em] aufgrund der Gutachten von Prof. Dr. Birgit Richter\\
\phantom{aufgrund der Gutachten} und Prof. Dr. Bj\o rn Ian Dundas.\\[2em]

Hamburg, den 24.7.2015 \\
Datum der Disputation: 26.6.2015 \newpage\clearpage \par\vspace*{.35\textheight}{\centering To Cedric\par} \newpage
\include{00-Introduction} \tableofcontents\thispagestyle{empty} \addtocontents{toc}{\protect\thispagestyle{empty}}  %unterdrueckt Seitenzahlen im Toc

\include{01-Monoidal} \include{02-MultBicat} \include{03-Deloop} 
\include{04-Uniqueness} \include{05-THH} \include{06-V1Kku} \clearpage \begin{thebibliography}{9999999}
\bibitem[Ad1]{Ad74} J. Adams, \emph{Stable Homotopy and Generalised Homology,} Univ. of Chicago Press, 1974, Reissued Edition 1995 
\bibitem[Ad2]{Ad69} J. Adams, \emph{Lectures on Generalised Cohomology,} Lec. Notes Math. \textbf{99}, 1969
\bibitem[AnHL]{AnHL} V. Angeltveit, M. Hill, T. Lawson, \emph{The Topological
Hochschild Homology of $\l$ and $ko$}, Am. J. Math. \textbf{132}(2), 2010, \arxiv{0710.4368}
\bibitem[AnR]{AnR} V. Angeltveit, J. Rognes, \emph{Hopf Algebra Structure on Topological 
Hochschild Homology}, Algebr. Geom. Topol. \textbf{5}, 2005, 1223–-1290, \arxivold{0502195}
\bibitem[A-Kku]{AuKku} C. Ausoni, \emph{On the Algebraic $K$-Theory of the Complex $K$-Theory 
Spectrum}, Inventiones mathematicae \textbf{180}(3), 2010, 611--668, \arxiv{0902.2334}
\bibitem[A-THH]{AuTHH} C. Ausoni \emph{Topological Hochschild Homology of Connective Complex 
$K$-Theory}, Am. J. Math. \textbf{127}(6), 2005, 1261--1313 %notarxiv
\bibitem[AR1]{AuQku} C. Ausoni, J. Rognes, \emph{Rational Algebraic $K$-Theory of 
Topological $K$-Theory}, Geom. Topol. \textbf{16}, 2012, 2037--2065, \arxiv{0708.2160}
\bibitem[AR2]{AuKl1} C. Ausoni, J. Rognes, \emph{Algebraic $K$-Theory of Topological $K$-Theory,}
Acta Math. \textbf{188}, 2002, 1--39
\bibitem[AR3]{AuKl2} C. Ausoni, J. Rognes, \emph{Algebraic $K$-Theory of the First Morava
$K$-Theory,} J. Eur. Math. Soc. \textbf{14}, 2011, 1041--1079, \arxiv{1006.3413}
\bibitem[ADR]{ADR} C. Ausoni, B. Dundas, J. Rognes, \emph{ Divisibility of the Dirac Magnetic 
Monopole as a Two-Vector Bundle over the Three-Sphere,} Doc. Math. \textbf{13}, 2008, 795--801
\bibitem[BDR]{BDR2004} N. Baas, B. Dundas, J. Rognes, \emph{Two-Vector Bundles and Forms of 
Elliptic Cohomology}, {London Mathematical Society Lecture Note Series
\textbf{308}}, 2004, 18--44, \arxivold{0306027}
\bibitem[BDRR1]{BDRR2011} N. Baas, B. Dundas, B. Richter, J. Rognes, \emph{Stable Bundles over 
Rig Categories}, {Journal of Topology \textbf{4}(3)}, 2011, 
623--640, \arxiv{0909.1742}
\bibitem[BDRR2]{BDRR2013} N. Baas, B. Dundas, B. Richter, J. Rognes, \emph{Ring Completion of 
Rig Categories}, {Journal f{\"u}r die reine und angewandte Mathematik 
(Crelles Journal) \textbf{674}}, 2013, 43--80, \arxiv{0706.0531}
\bibitem[BR1]{BaRi05} A. Baker, B. Richter, \emph{$\Gamma$-Cohomology of Rings of Numerical
Polynomials and $E_\infty$-Structures on $K$-Theory}, Comment. Math. Helv.
\textbf{80} (4), 2005, 691--723, \arxivold{0304473}
\bibitem[BR2]{BaRi08} A. Baker, B. Richter, \emph{Uniqueness of {$E_\infty$}-Structures for
Connective Covers}, Proc. Amer. Math. Soc. \textbf{136}, (2008), 707--714, \arxivold{0506422}
\bibitem[Ba]{Bar} C. Barwick, \emph{Multiplicative Structures on Algebraic $K$-Theory}, 
preprint \arxiv{1304.4867}, (2013)
\bibitem[Ben]{Bena} J. B\'enabou, \emph{Introduction to Bicategories}, in Reports of the Midwest
Category Seminar, Springer Berlin, 1967
\bibitem[Ber1]{Bergn1} J. Bergner, \emph{A Model Category Structure on the Category of Simplicial
Categories}, Trans. Amer. Math. Soc. \textbf{359}, 2007, 2043--2058, \arxivold{0406507}
\bibitem[Ber2]{Bergn2} J. Bergner, \emph{A Survey of $(\infty,1)$-Categories}, \arxivold{0610239}
\bibitem[Ber3]{Bergn3} J. Bergner, \emph{Models for Homotopical Higher Categories}, Talk at
the MSRI (Jan. 2014), \href{https://www.youtube.com/watch?v=q8J0bbaZnRM}{https://www.youtube.com/watch?v=q8J0bbaZnRM}
\bibitem[BGT1]{BGT2013} A. Blumberg, D. Gepner, G. Tabuada, \emph{A Universal Characterization
of Higher Algebraic $K$-theory}, {Geometry and Topology \textbf{17}}, 
2013, 733--838, \arxiv{1001.2282}
\bibitem[BGT2]{BGT} A. Blumberg, D. Gepner, G. Tabuada, \emph{Uniqueness of the 
Multiplicative Cyclotomic Trace}, to appear in Advances in Mathematics, \arxiv{1103.3923}, (2012)
\bibitem[BV]{BV} J. Boardman, R. Vogt, \emph{Homotopy Invariant Algebraic Structures on Topological
Spaces,} Springer Verlag Berlin, 1973
\bibitem[BLPRZ]{BLPRZ} I. Bobkova, A. Lindenstrauss, K. Poirier, B. Richter, I. Zakharevich,
\emph{On the Higher Topological Hochschild Homology of $\F_p$ and Commutative $\F_p$-Group
Algebras,} Proceedings of the BIRS workshop \emph{WIT: Women in Topology}, 2014
\bibitem[B1]{B1} M. B\"okstedt, \emph{Topological Hochschild Homology,} Unpublished
\bibitem[B2]{B2} M. B\"okstedt, \emph{The Topological Hochschild Homology of $\Z$ and $\Z/p$},
Unpublished
\bibitem[BM]{BMTCZ} M. B\"okstedt, I. Madsen, \emph{Topological Cyclic Homology of the
Integers,} Ast\'erisque \textbf{226}, 1994, 57--143
\bibitem[BHM]{BHMtr} M. B\"okstedt, W. Hsiang, I. Madsen, \emph{The Cyclotomic Trace and 
Algebraic $K$-Theory of Spaces}, Inventiones mathematicae \textbf{111}(1), 1993, 465--539 %noarxiv
\bibitem[BFV]{BFV} M. Brun, Z. Fiedorowicz, R. Vogt, \emph{On the Multiplicative 
Structure of Topological Hochschild Homology}, Algebraic \& Geometric 
Topology \textbf{7}, 2007, 1633–-1650, \arxivold{0410367}
\bibitem[BrRo]{BrRo05} R. Bruner, J. Rognes, \emph{Differentials in the Homological Homotopy Fixed
Point Spectral Sequence,} Alg. Geom. Topol. \textbf{5}, 2005, 653--690, \arxivold{0406081}
\bibitem[CCG]{CCG2010} P. Carrasco, A. Cegarra, A. Garz\'on, \emph{Nerves and Classifying 
Spaces for Bicategories}, Algebraic and Geometric Topology \textbf{10} 
(1), 2010, 219--274, \arxiv{0903.5058}
\bibitem[D1]{D98} B. Dundas, \emph{The Cyclotomic Trace for Symmetric Monoidal Categories,}
Geometry and Topology \AA rhus 1998, Contemp. Math. \textbf{258}, 2000, AMS, 121--143
\bibitem[D2]{D2} B. Dundas, \emph{The Cyclotomic Trace Preserves Operad Actions,} 2014, preprint
\bibitem[DGM]{DGM12} B. Dundas, T. Goodwillie, R. McCarthy, \emph{The Local Structure of 
Algebraic $K$-Theory}, Springer London, 2012 %noarxiv
%\bibitem[DK]{DK} W. Dwyer, D. Kan, \emph{Function Complexes in Homotopical Algebra},
%Topology \textbf{19}, 1980, 427--440
\bibitem[EKMM]{EKMM} A. Elmendorf, I. Kriz, M. Mandell, J.P. May, \emph{Rings, Modules,
and Algebras in Stable Homotopy Theory}, AMS Surveys and Monographs \textbf{47}, 1995
\bibitem[EM]{EM} A. Elmendorf, M. Mandell, \emph{Rings, Modules, and Algebras in 
Infinite Loop Space Theory}, Adv. Math. \textbf{205}, 2006, 163--228, \arxivold{0403403}
\bibitem[Gau\ss]{Gauss} C.F. Gau\ss, \emph{Disquisitiones Arithmeticae}, 
1801, Latin \href{http://edoc.hu-berlin.de/ebind/hdok2/h284\_gauss\_1801/pdf/h284\_gauss\_1801.pdf}{
http://edoc.hu-berlin.de/ebind/hdok2/h284\_gauss\_1801/pdf/h284\_gauss\_1801.pdf},\\ English
revised translation 1986, Springer New York 
\bibitem[GGN]{GGN} D. Gepner, M. Groth, T. Nikolaus, \emph{Universality of Multiplicative
Infinite Loop Space Machines}, preprint, \arxiv{1305.4550}
\bibitem[GSn]{GSn} D. Gepner, V. Snaith, \emph{Motivic Spectra Representing Cobordism and $K$-Theory,}
Documenta Math. \textbf{14}, 2009, 359--396, \arxiv{0712.2817}
\bibitem[GHOsT]{GHOsT} P. Goerss, M. Hopkins, \emph{Moduli Spaces of Commutative Ring Spectra,}
London Math. Soc. Lecture Notes \textbf{315}, 2004, 151--200
\bibitem[GJ]{GJ} P. Goerss, J. Jardine, \emph{Simplicial Homotopy Theory}, Birkh{\"a}user Basel, 2009 reprint %noarxiv
\bibitem[GGRSV]{GGRSV} Jo. Guccione, Ju. Guccione, M. Redondo, A. Solotar, O. Villamayor,
\emph{Cyclic Homology of Algebras with One Generator,} $K$-Theory \textbf{5}, 1991, 51--69
\bibitem[GJOs]{GJOs} N. Gurski, N. Johnson, A. Osorno, \emph{$K$-Theory for
$2$-Categories}, preprint, \arxiv{1503.07824}
%\bibitem[GPS]{GPS} R. Gordon, A. Power, R. Street, \emph{Coherence for Tricategories,} Mem. Amer. Math. Soc. \textbf{117} 
%(558), 1995
%\bibitem[GS]{GSch} P. Goerss, K. Schemmerhorn, \emph{Model Categories and Simplicial Methods,}
%Contemp. Math. \textbf{436}, 2077, 3--49, \arxivold{0609537}
\bibitem[J]{Joyal} A. Joyal, \emph{Quasi-Categories and Kan Complexes}, 
J. Pure Appl. Algebra \textbf{175}, 2002, 207--222 %noarxiv
\bibitem[JT]{JoyT} A. Joyal, M. Tierney, \emph{Quasi-Categories vs. Segal Spaces},
Contemp. Math. \textbf{431}, 2007, 277--326, \arxivold{0607820}
\bibitem[KV]{KV} M. Kapranov, V. Voevodsky, \emph{Braided Monoidal $2$-Categories
and Manin-Schechtman Higher Braid Groups,} J. Pure Appl. Algebra \textbf{92}, 1994, 241--267
\bibitem[Ko]{Kochm} S. Kochman, \emph{Bordism, Stable Homotopy and Adams Spectral Sequences,} Fields Institute Monographs, AMS, 1996
\bibitem[K]{K} H. K\"onig, \emph{The Segal Model as a Ring Completion and a Tensor 
Product of Permutative Categories}, PhD thesis, 2011, 
\href{http://ediss.sub.uni-hamburg.de/volltexte/2011/5032}{http://ediss.sub.uni-hamburg.de/volltexte/2011/5032}
\bibitem[LP]{LP2008} S. Lack, S. Paoli, \emph{2-Nerves for Bicategories},
{Journal of $K$-theory \textbf{38(2)}}, 2008, 153--175, \arxivold{0607271}
\bibitem[Lan]{L2011} M. Lange, \emph{Examples of Involutions on Algebraic $K$-Theory of
Bimonoidal Categories}, 2011, Diploma Thesis, available at\\
\href{http://www.math.uni-hamburg.de/home/richter/DA-Lange.pdf}{http://www.math.uni-hamburg.de/home/richter/DA-Lange.pdf}
\bibitem[Lap]{Lap} M. Laplaza, \emph{Coherence for Categories with Associativity, 
Commutativity and Distributivity}, Bull. AMS \textbf{78}, 1972, 220--222 %noarxiv
%\bibitem[Law]{Law} T. Lawson, \emph{Commutative $\Gamma$-Rings do not Model All 
%Commutative Ring Spectra}, Homology, Homotopy \& Applications \textbf{11.2}, 2009, 189--194, %noarxiv
\bibitem[Le]{Lei} T. Leinster, \emph{Basic Bicategories}, \arxivold{9810017}, 1998
\bibitem[Lo]{Loday} J.-L. Loday, \emph{Cyclic Homology}, Grundlehren \textbf{301}, Springer, 1992 %noarxiv
\bibitem[Lu1]{Lu1} J. Lurie, \emph{Higher Topos Theory}, Princeton University Press 
\textbf{170}, 2009, \arxivold{0608040}
\bibitem[Lu2]{Lu2} J. Lurie, \emph{Higher Algebra}, (August 2012) Preprint at\\ 
\href{http://www.math.harvard.edu/\textasciitilde lurie/papers/higheralgebra.pdf}{
http://www.math.harvard.edu/\textasciitilde lurie/papers/higheralgebra.pdf}
\bibitem[Lu]{LuStab} J. Lurie, \emph{Stable Infinity Categories}, \arxivold{0608228}
\bibitem[McL]{McL} S. Mac Lane, \emph{Homology,} 1995 reprint of the 1975 edition
\bibitem[MMSS]{MMSS} M. Mandell, J.P. May, S. Schwede, B. Shipley \emph{Model Categories of
Diagram Spectra}, Proceedings of the London Mathematical Society, \textbf{82}(2), 2001, 441--512 %noarxiv
\bibitem[MN]{MN} T. Masuda, T. Natsume, \emph{Cyclic Cohomology of Certain Affine Schemes,}
Publ. RIMS, Kyoto Univ. \textbf{21}, 1985, 1261--1279
\bibitem[May{$E_\infty$}]{MayEinf} J.P. May, \emph{$E_\infty$-ring spaces and $E_\infty$-ring spectra}, Lect. Notes Math. \textbf{577}, Springer Heidelberg, 1977 
\bibitem[May1]{MaySoat} J.P. May, \emph{Simplicial objects in algebraic topology}, Chicago Lect. in Math., Univ. Chicago Press, 1967
\bibitem[May2]{May2009} J.P. May, \emph{The Construction of $E_\infty$-Ring Spaces from 
Bipermutative Categories}, Geometry \& Topology Monographs \textbf{16}, 2009, 283--330, \arxiv{0903.2818}
\bibitem[MT]{MT1978} J.P. May, R. Thomason, \emph{The Uniqueness of Infinite Loop Space 
Machines}, {Journal of Topology \textbf{17}(3)}, 1978, 205--224%noarxiv
\bibitem[MSm]{MSm} J. McClure, J. Smith, \emph{Operads and Cosimplicial Objects: An Introduction,} 2004, \arxivold{0402117}
\bibitem[MS]{MS} J. McClure, R. Staffeldt, \emph{On the Topological Hochschild Homology
of} $bu$ I, Am. J. Math., 1993, 1--45 %noarxiv
\bibitem[MT]{MT} M. Mimura, H. Toda, \emph{Topology of Lie Groups I}, Transl. of Math. Mon. AMS, 2000
\bibitem[Oka]{Oka} S. Oka, \emph{Multiplicative Structure of Finite Ring Spectra and Stable
Homotopy of Spheres,} Alg. Top. \AA rhus 1982, Lecture Notes in Math. \textbf{1051}, 1984, 418--441
\bibitem[Os]{Os} A. Osorno, \emph{Spectra Associated to Symmetric Monoidal
Bicategories}, Algebraic and Geometric Topology, \textbf{12}(1), 2012, 307--342, \arxiv{1005.2227}
\bibitem[PR]{PRi} T. Pirashvili, B. Richter, \emph{Hochschild and Cyclic Homology via Functor Homology,} 
$K$-Theory \textbf{25} (1), 2002, 39--49 %noarxiv
\bibitem[Q1]{Q1971} D. Quillen, \emph{The Adams Conjecture}, {Journal of Topology \textbf{10}(1)}, 1971, 67--80 %noarxiv
\bibitem[Q2]{Q1972} D. Quillen, \emph{On the Cohomology and $K$-theory of the General Linear 
Groups over a Finite Field}, {Annals of Mathematics}, 1972, 552--586 %noarxiv
\bibitem[Q3]{Q1973} D. Quillen, \emph{Higher algebraic $K$-theory: I}, {Higher $K$-theories}, 1973, 85--147 %noarxiv
\bibitem[R]{Ri2010} B. Richter, \emph{An Involution on the $K$-theory of Bimonoidal 
Categories with Anti-Involution}, Algebraic and Geometric Topology \textbf{10}, (2010), 315--342, \arxiv{0804.0401}
\bibitem[Ro]{Rog14} J. Rognes, \emph{Chromatic Redshift,} \arxiv{1403.4838}
\bibitem[RSS]{RSS14} J. Rognes, S. Sagave, C. Schlichtkrull, \emph{Logarithmic Topological 
Hochschild Homology of Topological $K$-Theory Spectra}, preprint, \arxiv{1410.2170}, (2014)
\bibitem[Ros]{Ros1994} J. Rosenberg, \emph{Algebraic $K$-Theory and its Applications}, 1994 %noarxiv
\bibitem[Rot]{Rot2009} J. Rotman, \emph{An Introduction to Homological Algebra}, Springer New York, second edition 2009
\bibitem[Ru]{Rudy} Y. Rudyak, \emph{On Thom Spectra, Orientability, and Cobordism}, Springer Berlin Heidelberg, 1998
\bibitem[SaS]{SaSch14} S. Sagave, C. Schlichtkrull, \emph{Localization Sequences for
Logarithmic Topological Hochschild Homology}, preprint, \arxiv{1402.1317}, (2014) 
\bibitem[S]{S tr} C. Schlichtkrull, \emph{The Cyclotomic Trace for Symmetric Ring 
Spectra}, Geometry \& Topology Monographs \textbf{16}, 2009, 545--592, \arxiv{0903.3495}
\bibitem[Schm]{Schm} V. Schmitt, \emph{Tensor Product of Symmetric Monoidal Categories}, 2007, \arxiv{0711.0324}
\bibitem[SP]{SP09} C. Schommer-Pries, \emph{The Classification of Two-Dimensional Extended Topological Field Theories,}
PhD thesis, UC Berkeley 2009, \arxiv{1112.1000}
\bibitem[Schw1]{SchV0} S. Schwede, \emph{The Stable Homotopy Category is Rigid,} Ann. Math. \textbf{166}, 2007, 837--863
\bibitem[Schw2]{SchSym} S. Schwede, \emph{An untitled book project about symmetric spectra (version 2012)}, 
\href{http://www.math.uni-bonn.de/people/schwede/SymSpec.pdf}{http://www.math.uni-bonn.de/people/schwede/SymSpec.pdf}
\bibitem[Se]{Seg} G. Segal, \emph{Categories and Cohomology Theories}, Topology \textbf{13}(3), 1974, 293--312 %noarxiv
\bibitem[Se]{Serre} J.-P. Serre, \emph{Linear Representations of Finite Groups}, Springer New York, 1977%noarxiv
\bibitem[Sh]{ShTHH} B. Shipley, \emph{Symmetric Ring Spectra and Topological Hochschild 
homology}, $K$-Theory \textbf{19}(2), 2000, 155-–183, \arxivold{9801079}
\bibitem[Sn]{Sn} V. Snaith, \emph{Algebraic Cobordism And $K$-Theory,} Mem. Amer. Math. Soc. \textbf{221}, 1979
\bibitem[Str1]{Str} R. Street, \emph{Categorical Structures}, in Handbook of Algebra \textbf{1},
ed. M. Hazewinkel, Elsevier, 1996
\bibitem[Str2]{Str2} R. Street, \emph{The Algebra of Oriented Simplexes}, J. Pure Appl Alg. \textbf{49}(3), 1987, 283--335
\bibitem[Sw]{Sw} R. Switzer, \emph{Algebraic Topology - Homology and Homotopy}, Classics in Math., 
Springer Berlin Heidelberg, 2002 reprint %noarxiv
\bibitem[Tab]{Tab} G. Tabuada, \emph{Homotopy Theory of Spectral Categories}, Adv. Math.
\textbf{221(4)}, 2009, 1122--1143, \arxiv{0801.4524}
\bibitem[Th1]{Th1} R. Thomason, \emph{Symmetric Monoidal Categories Model All Connective 
Spectra}, Theory and Applications of Categories \textbf{1.5}, 1995, 78--118 %noarxiv
\bibitem[Th2]{Th2} R. Thomason, \emph{Homotopy Colimits in the Category of Small 
Categories}, Math. Proc. Cambridge Philos. Soc. \textbf{85.1}, 1979, 91--109 %noarxiv
\bibitem[Th3]{Th3} R. Thomason, \emph{$Cat$ as a Closed Model Category,} Cahiers Topologie G\'eom.
Diff\'erentielle \textbf{21}(3), 1980, 305--324
\bibitem[Toda]{Toda} H. Toda, \emph{On Spectra Realising Exterior Parts of the Steenrod Algebra,}
Topology \textbf{10}, 1971, 53--65
\bibitem[W]{WeiK} C. Weibel, \emph{The $K$-Book: An Introduction to Algebraic $K$-Theory},
Graduate Studies in Math. \textbf{145}, AMS, 2013
\bibitem[Z]{Z} S. Ziegenhagen, \emph{$E_n$-Cohomology as Functor Cohomology and
Additional Structures,} PhD thesis, 2014, \href{http://ediss.sub.uni-hamburg.de/volltexte/2014/6950}{
http://ediss.sub.uni-hamburg.de/volltexte/2014/6950}
\end{thebibliography}

\section*{Summary}\pagestyle{empty}
In this thesis I investigate the interaction of multiplicative and involutive structures
on algebraic $K$-theory of $E_\infty$-ring spectra. Algebraic $K$-theory is 
associated classically to discrete rings by a definition of Quillen \cite{Q1973} with
preceding approaches by Grothendieck, Bass and Milnor, who defined $K_0R$, $K_1R$ and $K_2R$ respectively.
Quillen identified algebraic $K$-theory as the homotopy groups of a space naturally associated
to a ring, unifying the first three definitions, and providing a
definition of $K_nR$ for all natural numbers. One approach to computations is the generalisation
of $K$-theory to more ringlike objects, yielding more induced structures
on $K$-theory, for instance multiplicative structures as described in \cite{EM,GGN,BGT,May2009} and 
involutions as defined in \cite{Ri2010}.

Driven by the main example, algebraic $K$-theory of the connective complex $K$-theory spectrum $ku$, and
building on the computations of Christian Ausoni in \cite{AuKku,AuTHH}, I focus on the induced multiplicative
structure on $K(ku)$ in chapters 1 to 3. Building on the delooping of permutative bicategories as developed
by Ang\'elica Osorno in \cite{Os}, I exhibit a tensor product on a bicategory of matrices $\M$ associated
to a bipermutative category $\R$ in chapter 2. By modifying 
the delooping of Osorno in chapter 3 I find an induced $E_\infty$-ring spectrum structure on $K(ku)$ by
identifying this spectrum as the Eilenberg-MacLane-spectrum associated to the bicategory of matrices
over finite-dimensional complex vector spaces. The involution as defined in \cite{Ri2010} easily
generalises to this setting, so I can exhibit the interaction of the involution with the multiplication
easily.

Since the calculations in \cite{AuKku,AuTHH} rely on trace methods, i.e., are obtained by careful
comparison of $K(ku)$ to topological Hochschild homology $THH(ku)$ along the trace map, I can use
the compatibility of the trace map with the multiplicative structures defined on both as a universal
property by the results of \cite{BGT2013,BGT}. This in particular implies that the trace map is
compatible with the involution defined on $K$-theory as in \cite{Ri2010} and on topological
Hochschild homology analogous to \cite{Loday}, giving the main result of chapter 5.

Finally in chapter 6 I investigate the involution on mod $(p,v_1)$ homotopy groups of $K(ku)$ as 
calculated in \cite{AuKku}. Specifically there is a subalgebra of $V(1)_*K(ku)$, which can be
understood purely in terms of the trace map $K(ku)\rightarrow THH(ku)$, and there are special
classes $\sigma_n$ as well as the ``higher Bott element'' $b$. For all of these I describe
the effect induced by complex conjugation on $ku$, and thus the induced involution on 
algebraic $K$-theory on $V(1)_*K(ku)$. 

\section*{Zusammenfassung}
In dieser Dissertation untersuche ich Multiplikationen und Involutionen auf algebraischer
$K$-Theorie von $E_\infty$-Ringspektren. Klassisch ist algebraische $K$-Theorie
eine Invariante diskreter Ringe definiert von Quillen in \cite{Q1973}. Quillen
vereinheitlicht Definitionen von Grothendieck, Bass und Milnor der Gruppen $K_iR$ f\"ur
$i=0,1,2$ in dieser Reihenfolge. Er definiert algebraische $K$-Theorie als Homotopiegruppen
eines nat\"urlich zu einem Ring $R$ assoziierten Raumes $BGL(R)^+$. Diese Definition vereinheitlicht
zugleich die vorher genannten Definitionen und gibt eine Definition f\"ur alle
nat\"urlichen Zahlen. Ein Zugang zu Berechnungen ist die Verallgemeinerung
von $K$-Theorie auf ringartige Objekte, was insbesondere Aufschluss gibt \"uber
induzierte Strukturen auf $K$-Theorie wie etwa Multiplikationen \cite{EM,GGN,BGT,May2009}
und Involutionen \cite{Ri2010}.

In den Kapiteln 1 bis 3 untersuche ich die multiplikative Struktur von $K(ku)$, die
durch die Identifikation entlang \cite{BDRR2011} als Delooping einer Bikategorie von 
Matrizen $\M$ induziert wird.
Genauer definiere ich in Kapitel 2 ein Tensorprodukt, das eine Multiplikation auf
$\M$ induziert, die sich mit der additiven Struktur, die Ang\'elica Osorno \cite{Os}
definiert, vertr\"agt. In Kapitel 3 beschreibe ich eine Variante ihres Deloopings
\cite{Os}, die durch das Tensorprodukt die Struktur eines $E_\infty$-Ringspektrums erh\"alt. 
Die von Birgit Richter in \cite{Ri2010} beschriebene Involution l\"asst sich
auf $\M$ erweitern, und wir erhalten, dass die Involution diese Multiplikation opponiert.

Die Berechnungen der mod $(p,v_1)$ Homotopiegruppen von Christian Ausoni in \cite{AuKku,AuTHH} basieren
grundlegend auf Spurmethoden, also einem sorgsamen Vergleich algebraischer $K$-Theorie mit topologischer
Hochschildhomologie. Die vergleichende Abbildung ist die Spur $K(ku)\rightarrow THH(ku)$, die ich 
mithilfe der Resultate aus \cite{BGT2013,BGT} als die universelle multiplikative nat\"urliche
Transformation $K\Rightarrow THH$ in Kapitel 5 definieren kann. Aus dieser Universalit\"at folgt
das Hauptresultat von Kapitel 5, dass sich die Spurabbildung auch mit der induzierten
Involution auf $K$-Theorie wie in \cite{Ri2010} beschrieben und der auf topologischer 
Hochschildhomologie zu der in \cite{Loday} analogen Involution vertr\"agt.

In Kapitel 6 untersuche ich die Involution auf mod $(p,v_1)$ Homotopiegruppen von $K(ku)$, wie sie aus
der Berechnung von \cite{AuKku} hervorgehen. Es gibt eine Unteralgebra in $V(1)_*K(ku)$, die sich vollst\"andig
\"uber die Spur in $V(1)_*THH(ku)$ verstehen l\"asst, sowie spezielle Elemente $\sigma_n$ und das
``h\"ohere Bott-Element'' $b$ in diesem Modul. F\"ur diese Klassen beschreibe ich die 
Involution auf $V(1)_*K(ku)$.

\newpage
\section*{Publications/Publikationen}
I have not published anything based on this thesis.\\
Es gibt keine Ver\"offentlichungen, die aus dieser Arbeit hervorgegangen sind.

\section*{Eidesstattliche Versicherung} Ich versichere an Eides statt, dass ich die Arbeit selbstst\"andig verfasst und 
keine anderen als die angegebenen Hilfsmittel und Quellen benutzt habe.\\[10ex]\flushright$\overline{\mathtt{Marc~Lange,}~
~~~~ \mathtt{Hamburg, ~24.7.2015}}$\end{document}
\grid
